### 2015-07-06 doc/thesis/evaluation.tex
More improvements to the description of evaluation categories

The \emph{poly} category shows the percentage of members that
we made minimal use of the dynamic type as a replacement for the
lack of type parameters.
For instance, the function \texttt{table.sort} from the Lua
standard library is in this category because it is a generic function.
This function sorts a given list of elements, which is a generic list.
However, we had to assign to this function the type
\texttt{(\{any\}, nil|(any, any) -> (boolean)) -> ()} because
Typed Lua does not have parametric polymorphism.

The \emph{over} category shows the percentage of members that
we gave a static type that is not precise enough,
as these members are overloaded functions that require intersection
types to describe their precise static types.
For instance, the function \texttt{math.abs} from the Lua
standard library is in this category because it has two types:
\texttt{(integer) -> (integer)} and \texttt{(number) -> (number)}.
This function returns the absolute value of a given number,
which can be either integer or float.
Even though we gave this function the more general type \texttt{(number) -> (number)},
it is not precise enough because the return type is always \texttt{number}
independently of the argument type.
In other words, the return type should be \texttt{integer} when
the argument type is also \texttt{integer}, and the return type
should be \texttt{number} when the argument type is also \texttt{number}.
However, we cannot give such a precise type to this function because
Typed Lua does not support overloaded functions.

The \emph{hard} category shows the percentage of members that
we could not give a precise static type.
For instance, the function \texttt{assert} from the Lua
standard library is in this category because it can return any number
of values of any type, being difficult to type this behavior.
Still, we gave this function the type \texttt{(value*) -> (any*)}.

>>>>

The \emph{poly} category shows the percentage of members that
we made minimal use of the dynamic type, as a replacement for the
lack of type parameters.
For instance, the function \texttt{table.sort} from the Lua
standard library is in this category because it is a generic function.
It sorts a given list of elements, which is a generic list.
However, we had to assign to this function the type
\texttt{(\{any\}, nil|(any, any) -> (boolean)) -> ()} because
Typed Lua does not support parametric polymorphism.
A better type for it would be
\texttt{(\{<T>\}, nil|(<T>, <T>) -> (boolean)) -> ()}.

The \emph{over} category shows the percentage of members that
require intersection types to describe their precise static types,
as they are overloaded functions.
For instance, the function \texttt{math.abs} from the Lua
standard library is in this category because it has two types:
\texttt{(integer) -> (integer)} and \texttt{(number) -> (number)}.
This function returns the absolute value of a given number,
which can be either integer or float.
Even though we gave this function the more general type \texttt{(number) -> (number)},
it is not precise enough because the return type is always \texttt{number}
independently of the argument type.
In other words, the return type should be \texttt{integer} when
the argument type is also \texttt{integer}, and the return type
should be \texttt{number} when the argument type is also \texttt{number}.
However, we cannot give such a precise type to this function because
Typed Lua does not support overloaded functions.

The \emph{hard} category shows the percentage of members that
do not fit in one of the previous categories, as they are difficult to type.
For instance, the function \texttt{string.format} from the Lua
standard library is in this category because it relies on format
strings, which are difficult to type.
Still, we gave this function the type \texttt{(string, value*) -> (string)}.
